### 2023-07-19 paper/sec-protonPDFs.tex
sect 2 revised
added nnpdf plot

\clearpage
\section{Constraints on proton structure}
\label{sec:protonPDFs}

@@

For the Hessian profiling studies based on the procedure of Sect.~\ref{sec:profiling}, the prior PDF set is taken to
be PDF4LHC21 NNLO, a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets (CT18~\cite{Hou:2019efy},
MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}).
%
The Hessian representations of PDF4LHC21 are obtained by means of the methodology developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
%
Being based on the combination of three modern global PDF fits, PDF4LHC21 provides a robust estimate
of  current uncertainties associated to our understanding of proton PDFs.
%
We profile PDF4LHC21 with various sets of LHC neutrino DIS projections in order to assess the stability
of the results with respect to its different inputs, such as charm-tagged structure functions.
%
A tolerance of $T = \sqrt{\Delta \chi^2}=3$ is adopted, corresponding to the average tolerance
used in the CT18 and MSHT20 Hessian determinations.
%
The consistent perturbative accuracy of the prior PDF set and the theoretical calculations entering
the pseudo-data generation is always accounted for.

@@

>>>>

\section{Constraints on proton structure}
\label{sec:protonPDFs}

@@

For the Hessian profiling studies based on the procedure of Sect.~\ref{sec:profiling}, the prior PDF set is taken to
be PDF4LHC21 NNLO, a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets (CT18~\cite{Hou:2019efy},
MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}).
%
The Hessian representations of PDF4LHC21 are obtained by means of the methodology developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
%
Being based on the combination of three modern global PDF fits, PDF4LHC21 provides a robust estimate
of  current uncertainties associated to our understanding of proton PDFs.
%
We profile PDF4LHC21 with various sets of LHC neutrino DIS projections in order to assess the stability
of the results with respect to its different inputs, such as charm-tagged structure functions.
%
The consistent perturbative accuracy of the prior PDF set and the theoretical calculations entering
the pseudo-data generation is always accounted for.

@@

Fig.~\ref{fig:nnpdf40_fasernu2_baseline} presents the same comparison
as in Fig.~\ref{fig:profiling_syst} now for
 the fits
 based on the NNPDF4.0 global analysis.
 %
 The impact on the PDFs found by direct inclusion of the FPF structure
 functions on the NNPDF4.0 fit is qualitatively consistent with
 that found from the Hessian profiling of PDF4LHC21.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.99\textwidth]{plots/FASERnu2-q100gev-ratios.pdf}
\caption{
  Same as Fig.~\ref{fig:profiling_syst} now for the fits
  based on the NNPDF4.0 global analysis.
%
}
\label{fig:nnpdf40_fasernu2_baseline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
